\documentclass[11pt]{article}
\usepackage[a4paper,margin=0.6in]{geometry}
\usepackage{fontspec}
\setmainfont{Calibri}
\usepackage[hidelinks]{hyperref}

\begin{document}

\begin{flushright}
\today
\end{flushright}

\noindent Michael Quick \\
\noindent Denfield, ON \\
\noindent 519-317-2635 \\
\noindent \href{mailto:mwquick04@gmail.com}{mwquick04@gmail.com} \\

\vspace{1em}

\noindent NAVBLUE \\
\noindent Madison Wilkinson, Head of Talent Acquisition\\
\noindent 400 Maple Grove Rd \\
\noindent Waterdown, ON, Canada\\

\vspace{1em}

\noindent Dear Madison Wilkinson,\\


I am writing to apply for the Software Developer Intern position at NAVBLUE, beginning in May 2025. As a third-year Computer Science student at Western University, I am seeking a 12–16 month co-op to deepen my software development expertise and contribute to the aviation industry’s digital transformation. NAVBLUE’s focus on innovative solutions, modern web technologies, and data-driven optimization aligns perfectly with my passion for combining robust engineering with real-world impact.\\

In my academic and professional experiences, I have consistently leveraged object-oriented programming principles (SOLID, DRY) and several languages, including C++, Python, JavaScript, and TypeScript. I am comfortable developing in Linux and Windows environments and have worked with frameworks such as React and Django for web development, as well as AGOpenGPS for embedded C++ in an autonomous tractor project. Through roles at Gruv Media and on-farm engineering with Hyland Farms, I acquired valuable experience integrating software solutions, troubleshooting complex systems, and documenting code for maintainability. This background has sharpened my debugging, testing, and collaborative skills—key attributes I am eager to bring to NAVBLUE’s development teams.\\

Beyond my technical skill set, I am highly motivated by NAVBLUE’s commitment to team-oriented development, continuous innovation, and a culture that balances excellence with inclusivity. Your emphasis on sharing ideas, working in cross-functional teams, and producing clear documentation resonates with my approach. I thrive in environments where I can learn from senior developers.\\

I would welcome the opportunity to further discuss how my experience and enthusiasm can complement NAVBLUE’s ongoing innovation efforts. Enclosed is my resume, which details my relevant coursework, professional experience, and side projects. Please feel free to contact me at 519-317-2635 or by email at \href{mailto:mwquick04@gmail.com}{mwquick04@gmail.com} to arrange an interview or request additional information.\\

Thank you for your consideration, and I look forward to the possibility of joining NAVBLUE as a Software Developer Intern.\\

\noindent Best regards,\\

\noindent Michael Quick

\end{document}
