\documentclass[11pt]{article}
\usepackage[a4paper,margin=0.75in]{geometry}
\usepackage{fontspec}
\setmainfont{Calibri}
\usepackage[hidelinks]{hyperref}

\begin{document}

\begin{flushright}
\today
\end{flushright}

\noindent Michael Quick \\
Denfield, ON \\
519-317-2635 \\
\href{mailto:mwquick04@gmail.com}{mwquick04@gmail.com} \\
\href{https://www.linkedin.com/in/michael-quick-467bb021b/}{linkedin.com/in/michael-quick-467bb021b/}

\vspace{1em}

\noindent Geotab \\
Ms. Sarah Lima \\
Oakville, ON, Canada

\vspace{1em}

\noindent Dear Ms. Lima:

\setlength{\parindent}{15pt}
\setlength{\parskip}{0.75em}

I am writing to express my keen interest in the Software Developer Intern position at Geotab, as advertised for the Spring/Summer 2025 term. As a third-year Computer Science student at Western University, I have built a strong foundation in data structures, algorithms, and software design principles that I am eager to apply in a challenging and innovative environment.

Throughout my academic career and personal projects, I have gained hands-on experience with both front-end and back-end development. I have built web applications using JavaScript and TypeScript, designed RESTful APIs, and explored various open-source technologies to create scalable and secure software solutions. My experience working in collaborative team environments, coupled with my commitment to writing well-designed, tested code, has prepared me to thrive in Geotab's dynamic setting.

What excites me most about Geotab is its leadership in IoT solutions and its impact on fleet management and data analytics. I am enthusiastic about the opportunity to contribute to projects that solve complex challenges for businesses worldwide and to work alongside a diverse team of innovators. I am confident that my technical skills, problem-solving mindset, and eagerness to learn will make me a valuable asset to your team.

Thank you for considering my application. I have enclosed my résumé for your review, and I welcome the opportunity to further discuss how my background aligns with Geotab’s goals. Please feel free to contact me at 519-317-2635 or via email at \href{mailto:mwquick04@gmail.com}{mwquick04@gmail.com}.

\setlength{\parindent}{0pt}

\vspace{1em}
Sincerely,

\vspace{1em}
Michael Quick

\end{document}
