\documentclass[11pt]{article}
\usepackage[a4paper,margin=0.75in]{geometry}
\usepackage{fontspec}
\setmainfont{Calibri}
\usepackage[hidelinks]{hyperref}

\begin{document}

\begin{flushright}
\today
\end{flushright}

\noindent Michael Quick \\
\noindent Denfield, ON \\
\noindent 519-317-2635 \\
\noindent \href{mailto:mwquick04@gmail.com}{mwquick04@gmail.com} \\

\vspace{1em}

\noindent Toronto Hydro \\
\noindent 14 Carlton Street \\
\noindent Toronto, ON, Canada

\vspace{2em}

\noindent Dear Hiring Team,

\setlength{\parindent}{15pt}
\setlength{\parskip}{0.75em}

I am pleased to submit my application for the Senior Technical Student role at Toronto Hydro. As a third-year Computer Science student with a strong background in data analytics and software engineering, I am excited by the opportunity to apply my quantitative, organizational, and communication skills within the regulatory analytics, rates and wholesale settlement department.

In my academic and professional experiences, I have developed advanced Excel capabilities, including building macros and pivot tables. Furthermore, I have gained exposure to Python for scripting and data wrangling, and I have started learning Alteryx and Tableau to build interactive dashboards. These tools have proven invaluable in managing large volumes of data and presenting insights visually—precisely the skills required to process daily and monthly wholesale settlement statements and perform regulatory research at Toronto Hydro.

Beyond my technical qualifications, I thrive in collaborative and fast-paced settings. At Gruv Media, for example, I worked with a cross-functional team to deliver time-sensitive software solutions and documented processes to ensure seamless handoffs between departments. This experience sharpened my written and verbal communication, as well as my ability to prioritize tasks effectively. I am confident that these skills, coupled with my analytical mindset and love for problem-solving, would allow me to excel in meeting deadlines while contributing meaningfully to your team’s data-driven decisions.

I am highly motivated by the prospect of joining Toronto Hydro, which is recognized for delivering safe and reliable electricity in Ontario. I look forward to bringing my enthusiasm for data analytics, strong organizational abilities, and proactive mindset to the Regulatory Analytics team. I would welcome the opportunity to discuss further how my skill set aligns with Toronto Hydro’s mission during an interview.

\setlength{\parindent}{0pt}

\vspace{1em}
Sincerely,

\vspace{1em}
Michael Quick

\end{document}
