\documentclass[11pt]{article}
\usepackage[a4paper,margin=0.6in]{geometry}
\usepackage{fontspec}
\setmainfont{Calibri}
\usepackage[hidelinks]{hyperref}

\begin{document}

\begin{flushright}
\today
\end{flushright}

\noindent Michael Quick \\
\noindent Denfield, ON \\
\noindent 519-317-2635 \\
\noindent \href{mailto:mwquick04@gmail.com}{mwquick04@gmail.com} \\

\vspace{1em}

\noindent L3Harris WESCAM \\
\noindent Hiring Manager, Software Engineering Co-op \\
\noindent 400 Maple Grove Rd \\
\noindent Waterdown, ON, Canada\\

\vspace{1em}

\noindent Dear Hiring Manager:\\

I am writing to express my strong interest in the Software Engineering Co-op opportunity at L3Harris WESCAM. As a third-year Computer Science student at Western University specializing in embedded systems and real-time programming, I am eager to contribute my C/C++ skills and hands-on hardware experience to support the development of cutting-edge optical sensor and targeting solutions.\\

Over the past years, I have honed my technical skills through academic projects and professional engagements. As a developer at Gruv Media, I employed Python and other technologies to build and maintain robust website and server solutions. Additionally, during my time at Hyland Farms, I developed and integrated a custom self-steering tractor solution using the open-source AGOpenGPS platform, which allowed me the opportunity to gain an in-depth understanding of hardware including sensors and wiring. These experiences have reinforced my attention to detail, collaborative mindset, and passion for developing quality software solutions.\\

What excites me about L3Harris WESCAM is the division’s focus on mission-critical technologies and solutions for defence and search-and-rescue operations. The role’s emphasis on embedded C/C++ programming and system testing aligns perfectly with my academic interests and hands-on experience. I am confident that my background in hardware-software integration, strong communication skills, and dedication to continuous learning will enable me to excel within your dynamic team.\\

I greatly appreciate your consideration. I welcome the opportunity to discuss how my skill set, motivation, and academic background can contribute to L3Harris WESCAM’s continued success. I can be contacted at 519-317-2635 or via email at \href{mailto:mwquick04@gmail.com}{mwquick04@gmail.com}. I look forward to the possibility of working with you and further developing my engineering career through this 16-month co-op opportunity.\\

\noindent Best regards,\\

\noindent Michael Quick

\end{document}
