\documentclass[11pt]{article}
\usepackage[a4paper,margin=0.75in]{geometry}
\usepackage{fontspec}
\setmainfont{Calibri}
\usepackage[hidelinks]{hyperref}

\begin{document}

\begin{flushright}
\today
\end{flushright}

\noindent Michael Quick \\
Denfield, ON \\
519-317-2635 \\
\href{mailto:mwquick04@gmail.com}{mwquick04@gmail.com} \\

\vspace{1em}

\noindent RouteThis \\
Sherima Ramcharan \\
165 King Street West, Unit 103 \\
Kitchener, ON, N2G 1A7

\vspace{1em}

\noindent Dear Sherima Ramcharan:

\setlength{\parindent}{15pt}
\setlength{\parskip}{0.75em}

I am writing to express my strong interest in the Software Developer Co-op position at RouteThis, scheduled to begin on May 5, 2025. As a dedicated Computer Science student at Western University with a passion for software development and innovative technology, I am eager to contribute to RouteThis’s mission of revolutionizing customer support through intelligent automation and connected experiences.

My academic background has provided me with a solid foundation in data structures, algorithms, and system design. I have gained practical experience through both academic projects and professional engagements, working with technologies such as Node.js, TypeScript, and React to develop scalable, well-tested applications. I am particularly excited about the opportunity to contribute to a fast-growing B2B software company that is transforming WiFi-connected homes and driving efficiency in a multi-billion-dollar industry.

I am drawn to RouteThis not only for its technical innovation but also for its collaborative culture and commitment to creative problem-solving. I am confident that my technical skills, proactive mindset, and dedication to quality code would make me a valuable addition to your team. For my co-op term, I would prefer a 16-month co-op, as I believe this extended duration will allow me to make a more significant impact while deepening my professional growth.

Thank you for considering my application. I have enclosed my résumé and transcript for your review and would welcome the opportunity to discuss how my background and skills can contribute to RouteThis’s continued success. Please feel free to contact me at 519-317-2635 or via email at \href{mailto:mwquick04@gmail.com}{mwquick04@gmail.com}.

\setlength{\parindent}{0pt}

\vspace{1em}
Sincerely,

\vspace{1em}
Michael Quick

\end{document}
