\documentclass[11pt]{article}
\usepackage[a4paper,margin=0.75in]{geometry}
\usepackage{fontspec}
\setmainfont{Calibri}
\usepackage[hidelinks]{hyperref}

\begin{document}

\begin{flushright}
\today
\end{flushright}

\noindent Michael Quick \\
Denfield, ON \\
519-317-2635 \\
\href{mailto:mwquick04@gmail.com}{mwquick04@gmail.com} \\
\href{https://www.linkedin.com/in/michael-quick-467bb021b/}{linkedin.com/in/michael-quick-467bb021b/}

\vspace{1em}

\noindent Trackunit \\
Emily Moroz \\
304 Talbot Street \\
London, ON, Canada

\vspace{1em}

\noindent Dear Emily Moroz:

\setlength{\parindent}{15pt}
\setlength{\parskip}{0.75em}

I am writing to express my keen interest in the Software Development Intern position at Trackunit for the Spring/Summer 2025 term, from May 5, 2025 to August 28, 2026. As a third-year Computer Science student at Western University with a strong foundation in data structures, algorithms, and software design, I am excited about the opportunity to contribute to Trackunit’s innovative IoT platform and help drive technological progress in the construction industry.

Throughout my academic career and hands-on projects, I have developed robust skills in both front-end and back-end development. I have gained practical experience with JavaScript and TypeScript through personal and school projects. I am particularly enthusiastic about leveraging modern tools, including AI and CI/CD pipelines, to write well-designed, tested code, and I value the importance of thorough peer code reviews in producing high-quality software.

What excites me most about Trackunit is your commitment to innovation in one of the largest industries in the world. I appreciate the balance between remote flexibility and in-person collaboration in your hybrid work environment, and I am eager to contribute my technical expertise, creativity, and problem-solving skills to a team that is passionate about enhancing operational efficiency across the construction sector.

Thank you for considering my application. I have enclosed my résumé and transcript for your review. I look forward to the possibility of discussing how my skills and experiences align with Trackunit’s mission and how I can contribute to your continued success. Please feel free to contact me at 519-317-2635 or via email at \href{mailto:mwquick04@gmail.com}{mwquick04@gmail.com}.

\setlength{\parindent}{0pt}

\vspace{1em}
Sincerely,

\vspace{1em}
Michael Quick

\end{document}
